---
title: "Challenge 7"
author: "Liu Yingzhe"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Creating plots  
a. Start with the penguins data frame
```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)
```

b. Map bill depth to the x-axis
c. Map bill length to the y-axis
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm))
```

d. Represent each observation with a point
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm)) +
geom_point()
```
e. Map species to the colour of each point
f. Title the plot "Bill depth and length"
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm,
                     colour = species)) +
geom_point() +
  labs(title = "Bill depth and length")

```

g. Add the subtitle "Dimensions for Adelie, Chinstrap, and
Gentoo Penguins"
h. Label the x and y axes as "Bill depth (mm)" and "Bill length
(mm)", respectively
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm,
                     colour = species)) +
geom_point() +
labs(title = "Bill depth and length",
subtitle = "Dimensions for Adelie, Chinstrap,and Gentoo penguins", 
x = "Bill depth (mm)",
y = "Bill length (mm)")

```
i. Label the legend "Species"
j. Add a caption for the data source
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm,
                     colour = species)) +
geom_point() +
labs(title = "Bill depth and length",
subtitle = "Dimensions for Adelie, Chinstrap,and Gentoo penguins", 
x = "Bill depth (mm)",
y = "Bill length (mm)", colour = "Species",
caption = "Source: Palmer Station LTER/ palmerpenguins" )


```
k. Finally, use a discrete colour scale that is designed to be color blind friendly 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm,
                     colour = species)) +
geom_point() +
labs(title = "Bill depth and length",
subtitle = "Dimensions for Adelie, Chinstrap,and Gentoo penguins", 
x = "Bill depth (mm)",
y = "Bill length (mm)", colour = "Species",
caption = "Source: Palmer Station LTER/ palmerpenguins") +
  scale_colour_viridis_d()
```

##Colour
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(penguins) + aes(x = bill_depth_mm, y = bill_length_mm,
                       colour = species) +
geom_point() + scale_colour_viridis_d()
```
##Shape
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, 
                     colour = species, shape = island)) +
geom_point() + scale_colour_viridis_d()

```
##Size
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = species,
size = body_mass_g)) +
geom_point() + scale_colour_viridis_d()
```
##Mapping vs setting 
Setting
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(penguins) +
aes(x = bill_depth_mm,
y = bill_length_mm) +
geom_point(size = 2, alpha = 0.5)
```

##Faceting
1. Grid
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(penguins) +
aes(x = bill_depth_mm,
y = bill_length_mm) +
geom_point() +
facet_grid(species ~ island)
```
2. Wrap
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_wrap(~ species)
```
3.Facet and colour 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
geom_point() + facet_grid(species ~ sex) + scale_color_viridis_d()
```


# Visualising numerical variables
##Loading data
```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(openintro)
glimpse(loans_full_schema)
```
##Select data
```{r, eval=TRUE,echo=TRUE}
# Enter code here
loans <- loans_full_schema %>%
select(loan_amount, interest_rate, term, grade,
state, annual_income, homeownership, debt_to_income)
glimpse(loans)
```
## Histograms and binwidth=1000
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = loan_amount)) +
geom_histogram(binwidth = 1000)
```

##Customizing histograms 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = loan_amount)) + geom_histogram(binwidth = 5000) +
labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club loans" )
```

##Fill with categorical variable 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
geom_histogram(binwidth = 5000, alpha = 0.5) +
labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans")
```

##Facet with categorical variable
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = loan_amount, fill = homeownership)) + geom_histogram(binwidth = 5000) +
labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans") +
facet_wrap(~ homeownership, nrow = 3)
```

#Density plots
## Adjusting bandwidth 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 1)
```

##customizing density plots 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 2) +
labs( x = "Loan amount ($)", y = "Density", title = "Amounts of Lending Club loans" )
```

##Adding categorical variable 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
geom_density(adjust = 2, alpha = 0.5) +
labs(x = "Loan amount ($)",y = "Density",title = "Amounts of Lending Club loans", fill = "Homeownership")
```
##Boxplots
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = interest_rate)) +
geom_boxplot()
```

##Customizing box plots 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = interest_rate)) +geom_boxplot() +labs(x = "Interest rate (%)",y = NULL,
title = "Interest rates of Lending Club loans") +
theme( axis.ticks.y = element_blank(), axis.text.y = element_blank() )
```

##Adding a categorical variable
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = interest_rate,
y = grade)) +
geom_boxplot() +
labs(x = "Interest rate (%)",y = "Grade",title = "Interest rates of Lending Club loans",subtitle = "by grade of loan")
```

#Scatterplot
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
geom_point()
```

##Hexplot
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
geom_hex()
```

#Visualising categorical variables
##Barplot 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = homeownership)) +
geom_bar()
```

##segmented bar plot 1
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = homeownership,
fill = grade)) +
geom_bar()

```

##segmented bar plot 2
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = homeownership, fill = grade)) +
geom_bar(position = "fill")
```
##customizing barplots 
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(y = homeownership, fill = grade)) + geom_bar(position = "fill") +
labs( x = "Proportion", y = "Homeownership", fill = "Grade", title = "Grades of Lending Club loans", subtitle = "and homeownership of lendee")
```
#visualising variables of various types 
##violin plots
```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(loans, aes(x = homeownership, y = loan_amount)) +
geom_violin()
```

##ridge plots
```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(ggridges)
ggplot(loans, aes(x = loan_amount, y = grade, fill = grade, color = grade)) +
geom_density_ridges(alpha = 0.5)

```




